---
title: "REddyProc Proccessing"
output: html_document
date: "2026-01-02"
---

# Load the necessary libraries 
```{r}
library(tidyverse)
library(dplyr)
library(amerifluxr)
library(devtools)
library(REddyProc)
library(bigleaf)
```



# Make a new dataset to work with for REddyProc to keep the original one unaltered and keep the years only 2024_2023
```{r}
REddy2004_2023 <- as.data.frame(Bart04_23AmeriFlux)
# Filter the dataframe to include only rows where Year is between 2004 and 2023
REddy2004_2023 <- REddy2004_2023[REddy2004_2023$Year >= 2004 & REddy2004_2023$Year <= 2023, ]

colnames(REddy2004_2023)
```

#Calculating the VPD from RH and Tair
```{r}
REddy2004_2023 <- cbind(REddy2004_2023, VPD = fCalcVPDfromRHandTair(REddy2004_2023$RH_F_1_1_1, REddy2004_2023$TA_F_1_1_1))
head(REddy2004_2023$VPD)
```


# Adding other neccessary columns here for REddyProc 
```{r}
REddy2004_2023$Rg <- PPFD.to.Rg(REddy2004_2023$PPFD_IN_F_1_1_1)
range(REddy2004_2023$Rg) # This range looks correct
REddy2004_2023$Tair <- REddy2004_2023$TA_F_1_1_1
REddy2004_2023$Ustar <- REddy2004_2023$USTAR_1_1_1
```



# now converting things to POSIX 
```{r}
# Make sure that all of these are in a numeric format
REddy2004_2023$Year   <- as.numeric(REddy2004_2023$Year)
REddy2004_2023$Month  <- as.numeric(REddy2004_2023$Month)
REddy2004_2023$Day    <- as.numeric(REddy2004_2023$Day)
REddy2004_2023$Hour   <- as.numeric(REddy2004_2023$Hour)
REddy2004_2023$Minute <- as.numeric(REddy2004_2023$Minute)

Bartlett.Posix.04_23 <- fConvertTimeToPosix(REddy2004_2023, 
                                           TFormat = 'YMDHM', 
                                           Year = 'Year', 
                                           Month = 'Month', 
                                           Day = 'Day', 
                                           Hour = 'Hour', 
                                           Min = 'Minute')
```

# Now making your SEddyProc class for ReddyProc and setting the location information
```{r}
Bart.BRT <- sEddyProc$new('US-Bar', Bartlett.Posix.04_23, c('NEE','Rg','Tair','VPD', 'Ustar'))
Bart.BRT$`.->sDATA`$sDateTime # REddyProc DateTime column that is created ends up being in the 15, 45 stamps, but when you export it, it is correct per what Thomas Wultzer said in his email.

# Set location information
Bart.BRT$sSetLocationInfo(LatDeg = 44.0646, LongDeg = -71.2881, TimeZoneHour = -5) 
```



# Here is the code for computing IQR:
```{r}
Bart.BRT$sMDSGapFill('NEE')
summary(Bart.BRT$sTEMP$NEE_orig)
summary(Bart.BRT$sTEMP$NEE_fall)

### Check for outliers using IQR of residuals (>6*IQR is outlier)
residual=Bart.BRT$sTEMP$NEE_orig-Bart.BRT$sTEMP$NEE_fall
IQR=IQR(residual,na.rm=TRUE)
outlier=ifelse(abs(residual)>(IQR*6),1,0)
NEE_filt=ifelse(outlier==0,Bart.BRT$sTEMP$NEE_orig,NA)
print(IQR)
summary(residual)
summary(outlier)
### Plot outliers
EddieC=data.frame(Bart.BRT$sTEMP$sDateTime,Bart.BRT$sTEMP$NEE_orig,Bart.BRT$sDATA$Ustar,Bart.BRT$sTEMP$NEE_fall,residual,outlier,NEE_filt)
colnames(EddieC)=c('sDateTime','NEE_orig','Ustar','NEE_fall','residual','outlier','NEE_filt')
### Number and Percentage of outliers
sum(as.numeric(EddieC$outlier),na.rm=TRUE)
sum(as.numeric(EddieC$outlier),na.rm=TRUE)/length(EddieC$outlier)

EddieC$year=substr(EddieC[,1],1,4)
EddieC$doy=strftime(EddieC[,1], format = "%j")
ggplot(EddieC,aes(y=NEE_orig,x=as.numeric(doy),color=as.factor(outlier)))+
  geom_point(shape=21,alpha=0.4)+
  theme_minimal()+
  labs(x='Day of year',y='NEE')+
  scale_color_manual(values=c('skyblue','navy'))+
  facet_wrap(~year)
summary(EddieC)

ggplot(EddieC,aes(y=abs(residual),x=Ustar,color=outlier))+
  geom_point()

### Re-run the outlier test after initial filtering
EddieC$residual2=EddieC$NEE_filt-EddieC$NEE_fall
EddieC$IQR2=IQR(EddieC$residual2,na.rm=TRUE)
EddieC$outlier2=ifelse(abs(EddieC$residual2)>EddieC$IQR2*6,1,0)
### Number and Percentage of outliers
sum(as.numeric(EddieC$outlier2),na.rm=TRUE)
sum(as.numeric(EddieC$outlier2),na.rm=TRUE)/length(EddieC$outlier2)

EddieC$NEE_filt2=ifelse(EddieC$outlier2==0,EddieC$NEE_filt,NA)
ggplot(EddieC,aes(y=abs(residual2),x=Ustar,color=outlier2))+
  geom_point()

### Remove outliers
Bart.BRT$sDATA$NEE=EddieC$NEE_filt2
```


# Continuing with REddyProc Processing

```{r}
Bart.BRT$sMDSGapFill("Tair", FillAll =FALSE)
Bart.BRT$sMDSGapFill("VPD", FillAll =FALSE)
Bart.BRT$sMDSGapFill("Rg", FillAll =FALSE)

set.seed(123456)
Bart.BRT$sEstimateUstarScenarios(nSample = 700L, probs = c(0.05, 0.5, 0.95))

##Not chaning my uStarTh for this, as I want the same uStar as my last run
uStarTh <- Bart.BRT$sGetEstimatedUstarThresholdDistribution()
uStar <- uStarTh  %>%
     filter( aggregationMode == "single") %>%
     select( "uStar", "5%", "50%", "95%")

uStarDf <- cbind(season=na.omit(unique(uStarTh$season)), uStar )
Bart.BRT$sSetUstarScenarios(uStarDf)
Bart.BRT$sGetUstarScenarios()

Bart.BRT$sMDSGapFillUStarScens('NEE')
```

# Now examining the Ustar filtering and adding it to the dataframe for BRT gap-filling
```{r}
REddy2004_2023$NEEIQR_orig <- Bart.BRT$`.->sDATA`$NEE

colnames(REddy2004_2023)
#check to make sure everything here passes the sniff check
print(sum(is.na(REddy2004_2023$NEE)))
print(sum(is.na(REddy2004_2023$NEEIQR_orig)))

# Just to make sure I am doing this instead
REddy2004_2023 <- REddy2004_2023 %>%
  mutate(
    NEEU05_orig = ifelse(Ustar >= 0.292441, NEEIQR_orig, NA),
    NEEU50_orig = ifelse(Ustar >= 0.3557708, NEEIQR_orig, NA),
    NEEU95_orig = ifelse(Ustar >= 0.4193314, NEEIQR_orig, NA)
  )


print(sum(is.na(REddy2004_2023$NEE)))
print(sum(is.na(REddy2004_2023$NEEIQR_orig)))
print(sum(is.na(REddy2004_2023$NEEU05_orig)))
print(sum(is.na(REddy2004_2023$NEEU50_orig)))
print(sum(is.na(REddy2004_2023$NEEU95_orig)))

write.csv(U05Input04_23, file = "~/Desktop/Python_XGB/NEE_U50_Python/AmeriFlux/U05Input04_23.csv")
write.csv(U50Input04_23, file = "~/Desktop/Python_XGB/NEE_U50_Python/AmeriFlux/U50Input04_23.csv")
write.csv(U95Input04_23, file = "~/Desktop/Python_XGB/NEE_U50_Python/AmeriFlux/U95Input04_23.csv")


#XGB final model parameters: 
# Start to run the optimizer ...
# XGBoost_regression took 464.40 seconds,  candidates checked: 40, best CV score: -2.098 ± 0.026
# Best parameters:
# OrderedDict([('colsample_bytree', 0.7538607571502197), ('learning_rate', 0.035310272828400296), ('max_depth', 6), ('n_estimators', 714), ('reg_alpha', 5.243049953323151), ('reg_lambda', 9.948506725979197), ('subsample', 0.7446697286156256)])
# Running: best_params=OrderedDict([('colsample_bytree', 0.7538607571502197), ('learning_rate', 0.035310272828400296), ('max_depth', 6), ('n_estimators', 714), ('reg_alpha', 5.243049953323151), ('reg_lambda', 9.948506725979197), ('subsample', 0.7446697286156256)])
# Data has been written to /Users/DarbyBergl/Desktop/Python_XGB/NEE_U50_Python/AmeriFlux/XGB_models/model_best_paramsDec18.csv
# Model pkl files saved to /Users/DarbyBergl/Desktop/Python_XGB/NEE_U50_Python/AmeriFlux/XGB_models/model04_23Dec18.pkl.
```






